Details matter: Similar-looking host galaxies can produce different merging compact binary populations

### 2015-05-28 paper/paper.tex
paper.tex: notes for later
paper.tex: More notes on BH birth spin and prompt collapse

>>>>

\section{Black hole spins in BH-NS binaries}

* References: review in Fragos and McClintock \cite{2015ApJ...800...17F}  and references therein (LMXBs) -- low birth
spins, because of stripped companions; for more on measurement, see \cite{2011CQGra..28k4009M}

* References on BH spin versus mass: angular momentum capture in prompt collapse: O'Connor and Ott and references
therein (note no fallback); note Ugliano has a differen result. See also Clausen et
al (probability of BH vs mass) for more recent
%O'Connor and Ott: a criteria for explosions http://arxiv.org/pdf/1010.5550v2.pdf...note they don't have fallback.
%Clausen et al: trying to find formation probability vs mass http://arxiv.org/pdf/1406.4869v2.pdf (assuming no binaries)
%...note also http://adsabs.harvard.edu/abs/2012ApJ...757...69U (which is complicated)

%* References: \cite{2013ApJ...762..104S}
